title: "Toronto's monthly Shelter Capacity Rate in 2020"
 
author: Ismael Gharbi
# date: 2024-01-23
abstract: "The political discourse, in Toronto in 2020, centered around the Housing crisis. One of the main talking points, were the overcrowdidness of homeless shelters in Toronto. This was percieved by the increased number of people sleeping on the streets.This paper's analysis may reveal that this pehenoma may be the result of the lack of efficient logistics rather than ressources "
format: pdf
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(palmerpenguins)
```


# Introduction

Github project repository:

https://github.com/ismaelgharbi0/Occupancy_rate_shelter_Toronto_2020

Since the start of the Covid pandemic in early 2020, many Torontonians were worried by the overcrowdedness of homeless shelters and the dangerous result of people sleeping on the streets during the Canadian Winter. They argued that an increased occupancy rate helped propogate and not contain the number of infections from the coronavirus in the biggest city in Canada. They argued that it may have contributed to the swift collapse of the Public Health System. Some placed the blame on the Ontario government for cutting spending on increasing shelter capacity for the people in need. Others argued it is a logistics issue and a product of mismanagement of the available ressources.


Over the course of the paper, the information on the occupancy and capacityof shelters in Toronto will originate from the Open Data Toronto website, created by the City of Toronto, will be investigated to build an analysis on the housing situation in Toronto. In Section 2: Data will be examined and analysed using a graph and a table. Section 3 will list the references and citations that supported the paper. 





# Data {#sec-data}

The data used in this paper is extracted from the Open Data Toronto website , provided by the City of Toronto. We have chosen this datasheet for the purpose of analysis as it lists the monthly occupancy and capacity of each shelter in Toronto in 2020 with clarity. Which helps the mission of finding the problem and may hint to how to fix this situation.

The raw data contained a long and detailed set of data as it shows for each shelter on a certain day of 2020, the name of the shelter,  the occupancy, the capacity and the occupancy/capacity  percentage ratio. 


```{r}
#| label: fig-planes
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

analysis_data <- read_csv(here::here("outputs/data/shelter_occupancy_2020.csv"))

analysis_data |> 
  ggplot(aes(x = width, y = length)) +
  geom_point(alpha = 0.8) +
  theme_minimal() +
  labs(x = "Wing width (mm)",
       y = "Wing length (mm)")
```


#Comment : Issue with the graph code please proceed

We see that the occupancy rate decreases over the months but never reaches 100%, which means there is always room to house homeless people in the shelter but it may demand a logistical solution instead of a material one.





# References
 [@citeR]

[@citetidyverse]

[@tellingstories]

[@citeODT]

[@citeHousingData]

[@citeReadR]

[@citeggplot2]

[@Toronto2023]






# References


